A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-01-16 pilot-publication/manuscript.Rmd
Add function to calculate iqr and add ISS and NISS to manuscript

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table
\@ref(tab:sample-characteristics). Overall, the number of females were
`r n.females` (`r p.females`%), the median age was `r median.age`
years (IQR `r iqr.age`)<!--, and the median ISS and NISS were X (IQR
	X) and X (IQR X) respectively-->. A total of `r n.m30d` (`r p.m30d`%)
patients had the primary outcome of mortality at 30 days after arrival
to the emergency department.

>>>>

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table
\@ref(tab:sample-characteristics). Overall, the number of females were
`r n.females` (`r p.females`%), the median age was `r median.age`
years (IQR `r iqr.age`), and the median ISS and NISS were `r median.iss`
(IQR `r iqr.iss`) and `median.niss` (IQR `iqr.niss`) respectively. A 
total of `r n.m30d` (`r p.m30d`%) patients had the primary outcome of 
mortality at 30 days after arrival to the emergency department.
